The Influence of Connectivity on Dung Beetle Communities

### 2025-07-24 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
some more

@@

**[Paragraph 7: spatial scale of experimental plots vs. dung detectability]** Finally, it is important to emphasize that while dung beetles are capable of long distance flight and detecting dung at distances of over X meters, the results I observed are lijkely not the result of a mismatch between the spatial scale of the experimental replicates and dung beetle movement. Put another way, some beetles were almost certainly drawn by the dung used in baits from the matrix into the plots. If this were a big effect we'd expect all plots to be similar to the matrix, or at least to each other. the fact that rectangular are lower suggests that...]

>>>>

Dung beetle biomass follows a pattern very similar to abundance where biomass is the highest in matrix plots, followed by connected, then winged, with a large drop in rectangle patches (Figure X). However, variation between individual beetle biomass  
is to large to detect a pattern in statistical analysis (Table X).

@@

**[Paragraph 7: spatial scale of experimental plots vs. dung detectability]**

Finally, it is important to emphasize that while dung beetles are capable of long distance flight and detecting dung at distances of over 50 meters *gray*, the results I observed are likely the result of a mismatch between the spatial scale of the experimental replicates and dung beetle movement. Put another way, some beetles were almost certainly drawn by the dung used in baits from the matrix into the plots. If this were a big effect we'd expect all plots to be similar to the matrix, or at least to each other. The fact that rectangular are lower suggests that some sort of landscape effect is apparent, likely related to habitat edge since connected and winged patches were the most similar.
